---
title: "IF-H (2023/2024)"
author: "plirapli"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Intro

1.  You may use either personal computer or lab's computer.
2.  Submit the knitted .pdf document.
3.  2 hours working duration + 5 minutes to submit.
4.  Close book, 1 A4 cheat sheet allowed.
5.  Googling, WhatsApp, ig, social media, and other communication media are prohibited.
6.  Bags and cell phones are placed in front.

Break a leg!

1.  Load library needed! Then use data 'movielens'! **point 2**

```{r No1}
# Answer
```

2.  Show the structure of Movielens data! **point 5**

```{r No2}
# Answer
```

Answer these questions!\
a. The Class of movielens object: ...\
b. Number of Observations: ...\
c. Number of Variables: ...\

3.  Implement a function that can be used if you only want to display the variable names of the movielens object! **point 5**

```{r No3}
# Answer
```

4.  Write a function to find out the data type of the genres variable, and explain at the bottom of the chunk why the genres variable uses that data type! **point 5**

```{r No4}
# Answer
```

explanation: **Genres use factor data type, because genres store a categorical data, such as "Action", "Comedy", "Romance", etc.**

5.  Show the last 5 observations of Movielens data! **point 5**

```{r No5}
# Answer
```

6.  Show movielens top 10 observations without movieId & userId variables, save them into an object named "tiny_df"! **point 15**

```{r no6}
# Answer
```

7.  Show the top 20 data with only romance genre, sorted by the highest rating.\
    Show data with title, year, genres, and rating variables only! **point 15**\
    Eliminate data with repeated titles (plus points) **point 5**

```{r no7}
# Answer
```

8.  Make a histogram with the x-axis the year the movie was made and the y-axis the frequency of the number of movies in that year.\
    Give the histogram a yellow color and a blue border and title it accordingly.\
    Below the chunk write the conclusion that can be drawn from your histogram! **point 13**

```{r No8}
# Answer
```

Conclusion: ...

9.  Classify the data of object "tiny_df" from question no 6 based on the rating with the following conditions:
    -   Rating less than 2 is categorized as "Negative"
    -   Rating more than 3 is categorized as "Positive"
    -   Ratings between the two conditions above are categorized as "Mixed" **point 15**

```{r No9}
# Answer
```

10. Add a new variable in the "tiny_df" data with a new column named "sentiment" that contains the implementation of number 9! **point 20**

```{r No10}
# Answer
```
